---
title: "Introduction to functions"
author: "20029"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp20029__ is a simple R package developed to bin multidimensional data into a two-way contingency table and construct density polygon of bivariate data. Two functions are provided, _bin2d_ (bin multidimensional data into a two-way contingency table) and _Dplot_ (construct density polygon of bivariate data). 

## _bin2d_
The source R code for _bin2d_ is as follows:
```{r,eval=FALSE}
bin2d<-function(x,column1,column2,WhetherNominal1=FALSE,WhetherNominal2=FALSE,breaks1 = "Sturges", breaks2 = "Sturges"){ 
  
  if (WhetherNominal1==FALSE){
    histg1 <- hist(x[,column1], breaks = breaks1, plot = FALSE) 
    br1 <- histg1$breaks
    mids1 <- histg1$mids
  }else {br1<-colnames(x)[column1];mids1 <-unique(x[,column2])}
  
  if (WhetherNominal2==FALSE){
    histg2 <- hist(x[,column2], breaks = breaks2, plot = FALSE) 
    br2 <- histg2$breaks
    mids2 <- histg2$mids
  }else {br2<-colnames(x)[column2];mids2 <-unique(x[,column2])}
  
  freq <- with(x,table(
    if (WhetherNominal1==FALSE) cut(x[,column1],br1) else get(br1), 
    if (WhetherNominal2==FALSE) cut(x[,column2],br2) else get(br2)))
  
  return(list(call = match.call(), freq = freq, breaks1 = br1, breaks2 = br2, mids1 = mids1, mids2 = mids2))
}
```

## _Dplot_
The source R code for _Dplot_ is as follows:
```{r,eval=FALSE}
Dplot<-function(x,breaks1 = "Sturges", breaks2 = "Sturges"){
  histg1 <- hist(x[,1], breaks = breaks1, plot = FALSE) 
  histg2 <- hist(x[,2], breaks = breaks2, plot = FALSE)
  br1 <- histg1$breaks
  br2 <- histg2$breaks
  freq <- table(cut(x[,1], br1), cut(x[,2], br2))
  h1 <- diff(br1) 
  h2 <- diff(br2)
  h <- outer(h1, h2, "*")
  Z <- freq / (n * h) # the density estimate
  persp(x=histg1$mids, y=histg2$mids, z=Z, shade=TRUE, xlab="Column1", ylab="Column2", zlab="density estimate",main="", theta=45, phi=30, ltheta=60)
}
```

